---
title: "JIMENA Parent Survey Data Tables"
execute:
  echo: false
  warnings: false
  error: false
format:   
    html:
        css: rcstyle.css
        theme: spacelab
        warning: false
        toc: true
        toc-depth: 3
        code-fold: true

---

```{r}
#| include: false
library(tidyverse)
library(rchelperfunctions)
library(janitor)
library(expss)
library(gt)

devtools::install_github("rosovconsulting/rchelperfunctions")
```


```{r}
#| include: false
survey_data <- read_rds("Data/277-04_JIMENA_Cleaned_Parent_Survey_Data_20250605.rds")

merged_col_map <- labelled::var_label(survey_data, null_action = "fill") %>% # use var_label to get variable names and labels
  as_tibble() %>% # set as tibble
  pivot_longer(cols = everything(),
               names_to = "Item",
               values_to = "Label") %>% # pivot the tibble into a longer format
  mutate(Label = gsub(pattern = '.*. - ', "", Label))

```


## Part I: Demographics

```{r}
survey_data %>% 
    tabyl(q1, show_na = FALSE) %>% 
    table_style(., "How many of your children attended this school?")

```

```{r}
survey_data %>% 
    tabyl(q2, show_na = FALSE) %>% 
    table_style(., "What is your relationship to your children at this school?")

```

```{r}
survey_data %>% 
    tabyl(q3, show_na = FALSE) %>% 
    table_style(., "Your gender")

```

```{r}
multi_response_table(survey_data, mdset_p("q4_\\d$")) %>% 
    mutate(q = str_remove(q, "^.+ - Selected Choice ")) %>% 
    multi_response_table_style() %>% 
    tab_header("Parent's Jewish Ethnicity")

```


```{r}
multi_response_table(survey_data, mdset_p("q5_\\d$")) %>% 
    mutate(q = str_remove(q, "^.+ - Selected Choice ")) %>% 
    multi_response_table_style() %>% 
    tab_header("Child's Jewish Ethnicity")

```

```{r}
multi_response_table(survey_data, mdset_p("q6_\\d\\d?$")) %>% 
    mutate(q = str_remove(q, "^.+ - Selected Choice ")) %>% 
    multi_response_table_style() %>% 
    tab_header("Child's Ancestral Origin")

```


```{r}
survey_data %>% 
    tabyl(q10, show_na = FALSE) %>% 
    table_style(., "What is your highest educational degree?")

```

```{r}
survey_data %>%
    select(matches("q11_\\d\\d?$")) %>% 
    likert_table() %>% 
    likert_table_style(., "Parent's Language Ability")
```

```{r}
survey_data %>% 
    tabyl(q13, show_na = FALSE) %>% 
    table_style(., "Family Synagogue Attendance")

```

```{r}
multi_response_table(survey_data, mdset_p("q14_\\d\\d?$")) %>% 
    mutate(q = str_remove(q, "^.+ - Selected Choice ")) %>% 
    multi_response_table_style() %>% 
    tab_header("Type of synagogue attended")

```

```{r}
survey_data %>% 
    tabyl(q15, show_na = FALSE) %>% 
    table_style(., "Sent to Jewish sleepaway camp")

```

```{r}
survey_data %>% 
    mutate(q16 = as.character(q16)) %>%
    mutate(q16 = na_if(q16, c("", "I don't remember", "n"))) %>% 
    tabyl(q16, show_na = FALSE) %>% 
    table_style(., "Sent to Jewish sleepaway camp")

```

```{r}
survey_data %>% 
    tabyl(q17, show_na = FALSE) %>% 
    table_style(., "Parent's Political Orientation")

```

## Part II: Children
```{r}
survey_data %>% 
    tabyl(q7, show_na = FALSE) %>% 
    table_style(., "Eldest Child's birthplace")

```

Somewhere else entries:
- 1 born in Israel; 3 born in America
- Mexico
```{r}
survey_data %>% 
    tabyl(q8, show_na = FALSE) %>% 
    table_style(., "Number of child's parents born in USA")

```

```{r}
survey_data %>% 
    tabyl(q9, show_na = FALSE) %>% 
    table_style(., "Number of child's grandparents born in USA")

```


```{r}
survey_data %>%
    select(matches("q12_\\d\\d?$")) %>% 
    likert_table() %>% 
    likert_table_style(., "Child's Language Ability")
```


```{r}
survey_data %>%
    select(matches("qid22_\\d\\d?$")) %>% 
    likert_table() %>% 
    likert_table_style(., "")
```

```{r}
survey_data %>%
    select(matches("qid24_\\d\\d?$")) %>% 
    likert_table() %>% 
    likert_table_style(., "")
```


```{r}
survey_data %>%
    select(matches("qid25_\\d\\d?$")) %>% 
    likert_table() %>% 
    likert_table_style(., "")
```


```{r}
survey_data %>%
    select(matches("qid26_\\d\\d?$")) %>% 
    likert_table() %>% 
    likert_table_style(., "")
```


```{r}
survey_data %>%
    select(matches("qid27_\\d\\d?$")) %>% 
    likert_table() %>% 
    likert_table_style(., "")
```

```{r}
survey_data %>%
    select(matches("qid28_\\d\\d?$")) %>% 
    likert_table() %>% 
    likert_table_style(., "")
```

```{r}
survey_data %>%
    select(matches("q35_\\d\\d?$")) %>% 
    likert_table() %>% 
    likert_table_style(., "")
```

## Part III: Open Ended Questions

### What are some ways that your school is inclusive of students from diverse ethnic and cultural backgrounds?
```{r}
open_ends_table(survey_data, q3_1)

```

### What are some ways that your school is not inclusive of students from diverse ethnic and cultural backgrounds?
```{r}
open_ends_table(survey_data, q3_2)

```

### What are some questions you have about inclusion of Sephardi/Mizrahi students and families?

```{r}
open_ends_table(survey_data, q3_3)

```

### What suggestions do you have for making your school more inclusive of Sephardi/Mizrahi students and families?
```{r}
open_ends_table(survey_data, q3_4)

```

## Part IV: Inclusion Score

```{r}
survey_data %>%
  filter(!is.na(inclusion_score)) %>%
  group_by(school) %>%
  summarise(
    valid_n = sum(!is.na(inclusion_score)),
    mean = mean(inclusion_score),
    sd = sd(inclusion_score),
    minimum = min(inclusion_score),
    maximum = max(inclusion_score)
  ) %>%
  ungroup() %>%
  gt::gt() %>%
  cols_label(
    valid_n = "Valid N",
    mean = "Mean",
    sd = "Standard Deviation",
    minimum = "Minimum",
    maximum = "Maximum"
  ) %>%
  fmt_number(
    columns = c(mean, sd),
    decimals = 2
  ) %>%
  gt::cols_align(align = "left", columns = 1) %>%
  tab_header("Inclusion Score by School") %>%
  gt::tab_style(
    style = list(
      gt::cell_text(color = "white", weight = "bold"),
      gt::cell_fill(color = "#5C068C")
    ),
    locations = gt::cells_title("title")
  ) %>%
  gt::tab_options(table.align = "left", data_row.padding = gt::px(5)) %>%
  gt::opt_table_lines()
    
  
```


## Part V: Items by Jewish Ethnicity and Ancestral Origin

```{r}
# survey_data %>%
#   select(q4_parent_ethnicity, matches("qid22_\\d\\d?$")) %>%
#   likert_table(cross = q4_parent_ethnicity) %>%
#   left_join(., merged_col_map) %>%
#   dplyr::select(-Item, -N) %>%
#   dplyr::select(Label, tidyselect::everything()) %>%
#   dplyr::rename(Item = Label) %>%
#   filter(!is.na(Group)) %>%
#   pivot_wider(
#     names_from = Group,
#     names_glue = "{.value}_{Group}",
#     values_from = c(
#       "Strongly agree",
#       "Agree",
#       "Neither agree nor disagree",
#       "Disagree",
#       "Strongly disagree"
#     )
#   ) %>%
#   gt::gt(rowname_col = "Item") %>% 
#   tab_spanner(
#     label = "Only Ashkenazi",
#     columns = ends_with("_Only Ashkenazi")) %>% 
#   tab_spanner(
#       label = "Sephardi/Mizrahi",
#       columns = ends_with("_Sephardi/Mizrahi")) %>% 
#   tab_spanner(
#       label = "Mixed Heritage",
#       columns = ends_with("_Mixed Heritage")) %>% 
#   tab_spanner(
#       label = "Not Jewish",
#       columns = ends_with("_Not Jewish"))
   
```

```{r}
ethnicity_tables = function(data, cross_var) {

  data %>%
    left_join(., merged_col_map) %>%
    dplyr::select(-Item) %>%
    dplyr::select(Label, tidyselect::everything()) %>%
    dplyr::rename(Item = Label) %>%
    filter(!is.na(Group)) %>%
    gt::gt(
      rowname_col = "Group",
      groupname_col = "Item",
      row_group_as_column = TRUE
    ) %>%
    fmt_percent(
      columns = where(is.numeric),
      decimals = 0
    ) 
}

```

```{r}
survey_data %>%
    select(q4_parent_ethnicity, matches("qid22_\\d\\d?$")) %>%
    likert_table(cross = q4_parent_ethnicity, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q4_parent_ethnicity) %>%
    tab_header("Parent's Jewish Ethnicity")
```


```{r}
survey_data %>%
    select(q5_child_ethnicity, matches("qid22_\\d\\d?$")) %>%
    likert_table(cross = q5_child_ethnicity, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q5_child_ethnicity) %>%
    tab_header("Child's Jewish Ethnicity")
```

```{r}
survey_data %>%
    select(q6_ancestral_origin, matches("qid22_\\d\\d?$")) %>%
    likert_table(cross = q6_ancestral_origin, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q6_ancestral_origin) %>%
    tab_header("Child's Ancestral Origin")
```


```{r}
survey_data %>%
    select(q4_parent_ethnicity, matches("qid24_\\d\\d?$")) %>%
    likert_table(cross = q4_parent_ethnicity, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q4_parent_ethnicity) %>%
    tab_header("Parent's Jewish Ethnicity")
```


```{r}
survey_data %>%
    select(q5_child_ethnicity, matches("qid24_\\d\\d?$")) %>%
    likert_table(cross = q5_child_ethnicity, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q5_child_ethnicity) %>%
    tab_header("Child's Jewish Ethnicity")
```

```{r}
survey_data %>%
    select(q6_ancestral_origin, matches("qid24_\\d\\d?$")) %>%
    likert_table(cross = q6_ancestral_origin, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q6_ancestral_origin) %>%
    tab_header("Child's Ancestral Origin")
```


```{r}
survey_data %>%
    select(q4_parent_ethnicity, matches("qid25_\\d\\d?$")) %>%
    likert_table(cross = q4_parent_ethnicity, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q4_parent_ethnicity) %>%
    tab_header("Parent's Jewish Ethnicity")
```


```{r}
survey_data %>%
    select(q5_child_ethnicity, matches("qid25_\\d\\d?$")) %>%
    likert_table(cross = q5_child_ethnicity, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q5_child_ethnicity) %>%
    tab_header("Child's Jewish Ethnicity")
```

```{r}
survey_data %>%
    select(q6_ancestral_origin, matches("qid25_\\d\\d?$")) %>%
    likert_table(cross = q6_ancestral_origin, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q6_ancestral_origin) %>%
    tab_header("Child's Ancestral Origin")
```




```{r}
survey_data %>%
    select(q4_parent_ethnicity, matches("qid26_\\d\\d?$")) %>%
    likert_table(cross = q4_parent_ethnicity, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q4_parent_ethnicity) %>%
    tab_header("Parent's Jewish Ethnicity")
```


```{r}
survey_data %>%
    select(q5_child_ethnicity, matches("qid26_\\d\\d?$")) %>%
    likert_table(cross = q5_child_ethnicity, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q5_child_ethnicity) %>%
    tab_header("Child's Jewish Ethnicity")
```

```{r}
survey_data %>%
    select(q6_ancestral_origin, matches("qid26_\\d\\d?$")) %>%
    likert_table(cross = q6_ancestral_origin, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q6_ancestral_origin) %>%
    tab_header("Child's Ancestral Origin")
```



```{r}
survey_data %>%
    select(q4_parent_ethnicity, matches("qid27_\\d\\d?$")) %>%
    likert_table(cross = q4_parent_ethnicity, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q4_parent_ethnicity) %>%
    tab_header("Parent's Jewish Ethnicity")
```


```{r}
survey_data %>%
    select(q5_child_ethnicity, matches("qid27_\\d\\d?$")) %>%
    likert_table(cross = q5_child_ethnicity, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q5_child_ethnicity) %>%
    tab_header("Child's Jewish Ethnicity")
```

```{r}
survey_data %>%
    select(q6_ancestral_origin, matches("qid27_\\d\\d?$")) %>%
    likert_table(cross = q6_ancestral_origin, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q6_ancestral_origin) %>%
    tab_header("Child's Ancestral Origin")
```



```{r}
survey_data %>%
    select(q4_parent_ethnicity, matches("qid28_\\d\\d?$")) %>%
    likert_table(cross = q4_parent_ethnicity, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q4_parent_ethnicity) %>%
    tab_header("Parent's Jewish Ethnicity")
```


```{r}
survey_data %>%
    select(q5_child_ethnicity, matches("qid28_\\d\\d?$")) %>%
    likert_table(cross = q5_child_ethnicity, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q5_child_ethnicity) %>%
    tab_header("Child's Jewish Ethnicity")
```

```{r}
survey_data %>%
    select(q6_ancestral_origin, matches("qid28_\\d\\d?$")) %>%
    likert_table(cross = q6_ancestral_origin, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q6_ancestral_origin) %>%
    tab_header("Child's Ancestral Origin")
```




```{r}
survey_data %>%
    select(q4_parent_ethnicity, matches("q35_\\d\\d?$")) %>%
    likert_table(cross = q4_parent_ethnicity, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q4_parent_ethnicity) %>%
    tab_header("Parent's Jewish Ethnicity")
```


```{r}
survey_data %>%
    select(q5_child_ethnicity, matches("q35_\\d\\d?$")) %>%
    likert_table(cross = q5_child_ethnicity, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q5_child_ethnicity) %>%
    tab_header("Child's Jewish Ethnicity")
```

```{r}
survey_data %>%
    select(q6_ancestral_origin, matches("q35_\\d\\d?$")) %>%
    likert_table(cross = q6_ancestral_origin, include_ns = FALSE) %>%
    ethnicity_tables(., cross_var = q6_ancestral_origin) %>%
    tab_header("Child's Ancestral Origin")
```





